\singlespacing
\begin{longtable}{lccp{2.5cm}p{2.5cm}p{6cm}}
\toprule
	Scan & Sample & Solution & Classification & Sweep Rate (mV/sec) & Description \\
	\midrule
	1 & 1018MS & H2SO4 & Ano/Cat & 1 mV/sec & Upward scan from 200 mV below CP to a potential above CP which produces 1 mA anodic current, followed by a reverse scan to return to the starting potential (200 mV below CP). \\
	2 & 1018MS & H2SO4 & LPR & 0.1 mV/sec & After Scan 1, potential held at 200 mV until stable current, followed by an upward scan from 20 mV below CP to 20 mV above CP and a downward scan to return to 20 mV below CP. \\
	3 & 1018MS & H2SO4 & Ano/Cat & 1 mV/sec & Upward scan from 200 mV below CP to a potential above CP which produces 10 mA anodic current, followed by a reverse scan to return to the starting potential (200 mV below CP). \\
	4 & 1018MS & H2SO4 & LPR & 0.1 mV/sec & After Scan 3, potential held at 200 mV until stable current, followed by an upward scan from 20 mV below CP to 20 mV above CP and a downward scan to return to 20 mV below CP. \\
	5 & 1018MS & HCl & Ano/Cat & 1 mV/sec & Upward scan from 200 mV below CP to a potential above CP which produces 1 mA anodic current, followed by a reverse scan to return to the starting potential (200 mV below CP). \\
	6 & 1018MS & HCl & LPR & 0.1 mV/sec & After Scan 5, potential held at 200 mV until stable current, followed by an upward scan from 20 mV below CP to 20 mV above CP and a downward scan to return to 20 mV below CP. \\
	7 & 1018MS & HCl & Ano/Cat & 1 mV/sec & Upward scan from 200 mV below CP to a potential above CP which produces 10 mA anodic current, followed by a reverse scan to return to the starting potential (200 mV below CP). \\
	8 & 1018MS & HCl & LPR & 0.1 mV/sec & After Scan 7, potential held at 200 mV until stable current, followed by an upward scan from 20 mV below CP to 20 mV above CP and a downward scan to return to 20 mV below CP. \\
	9 & 304SS & H2SO4 & Cathodic & 1 mV/sec & Downward scan from 20 mV above CP to ~700 mV below CP. \\
	10 & 304SS & H2SO4 & Anodic & 1 mV/sec & Upward scan from 20 mV below CP to the potential (~1700 mV vs. SCE) that achieves maximum potentiostat current (190 mA), followed by a downward scan until the sample surface changes from anodic to cathodic (i.e. current sign flips). \\
	11 & 304SS & HCl & Cathodic & 1 mV/sec & Downward scan from 20 mV above CP to ~700 mV below CP. \\
	12 & 304SS & HCl & Anodic & 1 mV/sec & Upward scan from 20 mV below CP to the potential (~400 mV vs. SCE) that achieves maximum potentiostat current, followed by a downward scan until the sample surface changes from anodic to cathodic (i.e. current sign flips).  Since the current in this sample/solution combination may continue to increase after switching scan direction, the direction was reversed in the vicinity of 100 mA instead of the maximum current (190 mA). \\
	\bottomrule
	\caption{Description of parameters for the 12 collected polarization curves.}
	\label{table:sweeps_full}
\end{longtable}
\doublespacing
